Comparison Of Several Sequential And Parallel Derivative-free Global Optimization Algorithms

### 2019-04-30 2019/PAVT/pavt_paper.tex
PAVT: update table with speedups
PAVT: final fixes

An anomalous superlinear speedup of MIDACO in time on the GKLS 2d Hard class when
employing 8 and 12 nodes can be explained by the fact that, according to Table \ref{tab:iterations},
MIDACO has solved a greater number of problems in the parallel mode than in the sequential one,
hence, has worked until the limit of trials is expired on a less number of problems.

@@

\begin{table}
  \centering
  \caption{Speedup of parallel computations executed by the parallel algorithms}
  \label{tab:speedup}
  \begin{tabular}{cccccccc}
    \cline{3-8}\noalign{\smallskip}
    \multicolumn{2}{c}{  } & \textit{p} & \multicolumn{2}{c}{Globalizer} & &
\multicolumn{2}{c}{MIDACO}   \\
    \noalign{\smallskip} \cline{4-5} \cline{7-8}  \noalign{\smallskip}
    \multicolumn{2}{c}{  } & & \textit{Simple} & \textit{Hard} & & \textit{Simple} &
\textit{Hard}  \\
    \noalign{\smallskip}\hline
I  & \textbf{1 cluster node}  %\multirow{3}{*}{}
    & \textit{1}   & 25270 (27.3s) & 55180 (61.8s) & & 27645 (32.2s) & 72068 (132.5s)  \\
  &  & \textit{16} & 14.3(11.7) & 14.9(12.6)  & &  16.9(14.4) & 16.7(14.4) \\
  \hline \noalign{\smallskip}
II  & \textbf{2 cluster nodes}  %\multirow{3}{*}{}
  & \textit{1}      &   1.9(1.9) & 2.4(2.2)  & & 2.6(1.7) & 2.7(2.3) \\
  &   & \textit{16} & 34.5(20.4) & 31.4(18.8) & & 24.5(18.8) & 32.0(29.1) \\
    \noalign{\smallskip}\hline	\noalign{\smallskip}
III  & \textbf{4 cluster nodes}  %\multirow{3}{*}{}
& \textit{1}      & 5.0(4.6) & 4.3(4.1) & & 4.8(3.9) & 4.5(4.4) \\
&   & \textit{16} & 68.8(23.7) & 71.2(25.8) & & 52.3(32.9) & 57.0(50.2) \\
  \noalign{\smallskip}\hline	\noalign{\smallskip}
VI & \textbf{8 cluster nodes} %\multirow{3}{*}{}
& \textit{1}    & 12.0(8.7) & 10.9(8.3) & & 9.7(8.2)    & 7.3(9.0)    \\
& & \textit{16} & 174.1(4.7) & 177.8(5.3) & & 101.6(51.6) & 93.1(84.1) \\
    \noalign{\smallskip}\hline
    V & \textbf{12 cluster nodes} %\multirow{3}{*}{}
    & \textit{1}    & 21.9(11.4)  & 23.0(12.8)  & & 12.4(11.1)  & 12.0(14.8)  \\
    & & \textit{16} & 333.5(2.7) & 347.9(3.0) & & 164.5(82.0) & 183.2(129.7) \\
        \noalign{\smallskip}\hline
  \end{tabular}
\end{table}

>>>>

An anomalous superlinear speedup of MIDACO in time on the GKLS 2d Hard class when
employing 8 and 12 nodes can be explained by the fact that, according to Table \ref{tab:iterations},
MIDACO has solved a greater number of problems in the parallel mode than in the sequential one,
hence, it has performed much less iterations than in sequential mode.

@@

\begin{table}
  \centering
  \caption{Speedup of parallel computations executed by the parallel algorithms}
  \label{tab:speedup}
  \begin{tabular}{cccccccc}
    \cline{3-8}\noalign{\smallskip}
    \multicolumn{2}{c}{  } & \textit{p} & \multicolumn{2}{c}{Globalizer} & &
\multicolumn{2}{c}{MIDACO}   \\
    \noalign{\smallskip} \cline{4-5} \cline{7-8}  \noalign{\smallskip}
    \multicolumn{2}{c}{  } & & \textit{Simple} & \textit{Hard} & & \textit{Simple} &
\textit{Hard}  \\
    \noalign{\smallskip}\hline
I  & \textbf{1 cluster node}  %\multirow{3}{*}{}
    & \textit{1}   & 25270 (27.3s) & 55180 (61.8s) & & 27645 (32.2s) & 72068 (132.5s)  \\
  &  & \textit{16} & 14.3x(11.7x) & 14.9x(12.6x)  & &  16.9x(14.4x) & 16.7x(14.4x) \\
  \hline \noalign{\smallskip}
II  & \textbf{2 cluster nodes}  %\multirow{3}{*}{}
  & \textit{1}      &   1.9x(1.9x) & 2.4x(2.2x)  & & 2.6x(1.7x) & 2.7x(2.3x) \\
  &   & \textit{16} & 34.5x(20.4x) & 31.4x(18.8x) & & 24.5x(18.8x) & 32.0x(29.1x) \\
    \noalign{\smallskip}\hline	\noalign{\smallskip}
III  & \textbf{4 cluster nodes}  %\multirow{3}{*}{}
& \textit{1}      & 5.0x(4.6x) & 4.3x(4.1x) & & 4.8x(3.9x) & 4.5x(4.4x) \\
&   & \textit{16} & 68.8x(23.7x) & 71.2x(25.8x) & & 52.3x(32.9x) & 57.0x(50.2x) \\
  \noalign{\smallskip}\hline	\noalign{\smallskip}
VI & \textbf{8 cluster nodes} %\multirow{3}{*}{}
& \textit{1}    & 12.0x(8.7x) & 10.9x(8.3x) & & 9.7x(8.2x)    & 7.3x(9.0x)    \\
& & \textit{16} & 174.1x(4.7x) & 177.8x(5.3x) & & 101.6x(51.6x) & 93.1x(84.1x) \\
    \noalign{\smallskip}\hline
    V & \textbf{12 cluster nodes} %\multirow{3}{*}{}
    & \textit{1}    & 21.9x(11.4x)  & 23.0x(12.8x)  & & 12.4x(11.1x)  & 12.0x(14.8x)  \\
    & & \textit{16} & 333.5x(2.7x) & 347.9x(3.0x) & & 164.5x(82.0x) & 183.2x(129.7x) \\
        \noalign{\smallskip}\hline
  \end{tabular}
\end{table}
